Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-10 thesis/chapters/ch_conclusion.tex
new dissertation command

In ongoing work we are extending these methods by implementing them in cosmological simulations of UFD galaxy evolution. Our detailed model tracking the feedback and yields from individual stars will build substantially upon recent works investigating metal enrichment at high redshift and in UFDs and their progenitors \citep[e.g.][]{Ritter2015,Jeon2017,Corlies2018,Wheeler2018,Agertz2019}. This work includes additional improvements to the simulations presented in this \dissertation, including a model for Pop III star formation and chemical enrichment adapted from \cite{Wise2012a}, a new IMF sampling scheme that allows us to follow very low mass stars ($M_* \lesssim 2$~M$_{\odot}$) -- which have no significant feedback or metal enrichment, but are important long-lived tracers of galactic chemical enrichment -- aggregated together into a single particle during each star formation event, improvements to the numerical implementation to ease memory consumption in these significantly larger simulations, and new metal tracer fields to follow the contribution of AGB, core collapse SNe, Type Ia SNe, and PopIII stars to the total metal content of each cell independently.

>>>>

In ongoing work we are extending these methods by implementing them in cosmological simulations of UFD galaxy evolution. Our detailed model tracking the feedback and yields from individual stars will build substantially upon recent works investigating metal enrichment at high redshift and in UFDs and their progenitors \citep[e.g.][]{Ritter2015,Jeon2017,Corlies2018,Wheeler2018,Agertz2019}. This work includes additional improvements to the simulations presented in this \Dissertation, including a model for Pop III star formation and chemical enrichment adapted from \cite{Wise2012a}, a new IMF sampling scheme that allows us to follow very low mass stars ($M_* \lesssim 2$~M$_{\odot}$) -- which have no significant feedback or metal enrichment, but are important long-lived tracers of galactic chemical enrichment -- aggregated together into a single particle during each star formation event, improvements to the numerical implementation to ease memory consumption in these significantly larger simulations, and new metal tracer fields to follow the contribution of AGB, core collapse SNe, Type Ia SNe, and PopIII stars to the total metal content of each cell independently.
